Re-fit

### 2022-09-09 scripts/r/04_refit/refit_tr.Rmd
fixed typo
Use here for paths to avoid copy/pasting millions of lines of code

# libs
library(tidyverse)
library(brms)
library(readxl)

@@

path <- "./data/analyses/tr/trachyphyllia_lappa"

@@

MSA_combined <- readRDS("./data/analyses/tr/alosa_atun/alosa_atun_data.rds", refhook = NULL)

@@

@@

path <- "./data/analyses/tr/dunkleosteus_inscriptus/data/"

flist_times  <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^timings(.*)xlsx")
get_times    <- lapply(paste0(path, flist_times), read_excel)
times        <- bind_rows(get_times)

flist_trials <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^trials(.*)xlsx")
get_trials   <- lapply(paste0(path, flist_trials), read_excel)
trials       <- bind_rows(get_trials)

@@

dunkleosteus_inscriptus_5_npdur_cat <- brm(
  dur_a_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_5_npdur_cat"
  )

@@

#################
### Load data ###
#################
d <- read_delim("./data/analyses/tr/chelonia_brummeri/analysis/german_msa_prosody.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
syll <- read_csv("./data/analyses/tr/chelonia_brummeri/analysis/syllables.csv")

@@

# read csv
msa_data_raw <- read_csv("./data/analyses/tr/procambarus_mahogoni/MSA-data.csv")

>>>>

# libs
library(tidyverse)
library(brms)
library(readxl)
library(lme4)

@@

path <- here("data", "analyses", "tr", "trachyphyllia_lappa")

@@

MSA_combined <- readRDS(here("data", "analyses", "tr", "alosa_atun", "alosa_atun_data.rds"), refhook = NULL)

@@

data = read.csv(here("data", "analyses", "tr", "pervagor_meeki", "Data", "ManySpeech_Praat_merged_data.csv"), header=T)

@@

path <- here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data/")

flist_times  <- list.files(path = here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data"), pattern = "^timings(.*)xlsx")
get_times    <- lapply(paste0(path, flist_times), read_excel)
times        <- bind_rows(get_times)

flist_trials <- list.files(path = here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data"), pattern = "^trials(.*)xlsx")
get_trials   <- lapply(paste0(path, flist_trials), read_excel)
trials       <- bind_rows(get_trials)

@@

dunkleosteus_inscriptus_5_npdur_cat <- brm(
  dur_np_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_5_npdur_cat"
  )

@@

#################
### Load data ###
#################
d <- read_delim(here("data", "analyses", "tr", "chelonia_brummeri", "analysis", "german_msa_prosody.txt"), delim = "\t", escape_double = FALSE, trim_ws = TRUE)
syll <- read_csv(here("data", "analyses", "tr", "chelonia_brummeri", "analysis", "syllables.csv"))

@@

# read csv
msa_data_raw <- read_csv(here("data", "analyses", "tr", "procambarus_mahogoni", "MSA-data.csv"))
